ggplot and the venn diagram for the lefse bars !

### 2020-12-18 scripts/44_ggplot_venn_lefse.Rmd
gosh cant believe how much im learning purrr right now

pres_all_list <- pres_all %>% 
  split(., list(.$outcome)) %>% 
  split(~ split())
  map(~ pull(.data = ., pathway))

all_names <- names(pres_all_list) 
icans <- all_names[str_detect(all_names, 'icans')]
icans_list <- pres_all_list %>% 
  pluck(icans)
```

@@

ggvenn(pres_all_list[[icans]])
```

>>>>

pres_all_list <- pres_all %>% 
  split(., list(.$cohort, .$outcome )) %>% 
  map(~ pull(.data = ., pathway)) %>% 
  compact()

vars <- pres_all %>% 
  distinct(outcome) %>% 
  pull(outcome)

pres_all_list_every <- vars %>% 
  set_names(vars) %>% 
  map(function(var){
    pres_all_list %>% 
        keep(.p = str_detect(names(.), var))
  } )
```

@@

pres_all_list_every %>% 
  imap(~ ggvenn(.x) +
         #labs(title = str_glue('{.y}')) +
          ggsave(str_glue('../figs/venn_pathway_{.y}.pdf'), width = 7, height = 4))
```
